\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

% Encoding & fonts (improves PDF text extraction)
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Colors & formatting
\definecolor{linkblue}{RGB}{0,102,204}
\titleformat{\section}{\large\bfseries\color{linkblue}}{}{0em}{}[\titlerule]
\pagestyle{empty}
\setlength{\parindent}{0pt}

% Macros
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\textbf{#1} \hfill {#2}\\
  {\small#3} \hfill {\small\textit{#4}}\\[-4pt]
}

\begin{document}

%========= HEADER =========
\begin{center}
  {\LARGE\bfseries Kadiri Mohan Kumar}\\
  \vspace{3pt}
  \small
  Software Engineer \textbar{} Backend \& Security \textbar{} System Design Enthusiast\\
  \href{mailto:kadirimohankumar1709@gmail.com}{kadirimohankumar1709@gmail.com} \textbar{} +91-74165-32127 \textbar{} Hyderabad, India\\
  \href{https://mohankumarkadiri.vercel.app}{Portfolio} \textbar{} \href{https://github.com/mohankumarkadiri}{GitHub} \textbar{} \href{https://www.linkedin.com/in/mohankumarkadiri/}{LinkedIn}
\end{center}

%===== SUMMARY =====
\section*{Summary}
Software Engineer with 2+ years of experience building secure, scalable backends using Node.js, Python, Docker, and AWS. Strong background in data structures and algorithms with competitive programming experience (550+ LeetCode problems, top 1\%). Developed production-level tools used by global teams. Active open source contributor, enthusiastic about system design, performance tuning, and developer productivity.

%===== EXPERIENCE =====
\section*{Experience}
\resumeSubheading{Uptycs}{Jun 2023 -- Present}{Security Solutions Engineer}{Hyderabad, India}
\begin{itemize}[leftmargin=*,itemsep=2pt]
  \resumeItem{Developed and deployed \textbf{IBM QRadar apps} for endpoint telemetry visualization, now used by 10+ enterprise clients.}
  \resumeItem{Developed \textbf{third-party integrations} (Splunk, GsecOps) to export detections and alerts, used by more than 95\% of the customers.}
  \resumeItem{Built automation pipelines with \textbf{AWS Lambda (Python/Node.js)} to process and forward alerts, reducing manual operations by 40\%.}
  \resumeItem{Integrated \textbf{Slack, Jira, Zoho APIs} for real-time alerting and triage, cutting incident response times by 50\%.}
  \resumeItem{Built internal tool using React.js and Node.js to automate data migration, reducing manual effort by \textbf{60\%}.}
  \resumeItem{Implemented \textbf{SQL-based dynamic asset} tagging workflows, reducing manual tagging overhead by 50\%.}
  \resumeItem{Helped \textbf{10+} clients to export detections via Uptycs APIs to Splunk and S3.}
\end{itemize}

%===== PROJECTS =====
\section*{Projects}
\textbf{Real-Time Collaborative Code Editor} \hfill \href{https://github.com/mohankumarkadiri/collab-code-editor}{GitHub}
\vspace{6pt}
\begin{itemize}[leftmargin=*,itemsep=2pt]
  \resumeItem{Built Google-authenticated, invite-only collaborative IDE with React, Monaco Editor and Socket.IO, supporting 50+ concurrent users.}
  \resumeItem{Implemented room-based access control and OAuth2 flow, preventing 100\% unauthorized joins.}
  \resumeItem{Used Redis for session and socket mapping, reducing lookup time by 70\%.}
  \resumeItem{Synced language changes in real time. The host can change the coding language and guests follow instantly.}
  \resumeItem{Handled network interruptions with auto-reconnect and session recovery, improving reliability by 60\%.}
  \resumeItem{Containerized client and server with Docker Compose and .env configs, cutting setup time by 80\%.}
  \resumeItem{Persisted user editor settings (theme, font size, tab width, wrap, minimap) in MongoDB for consistent experience.}
  \resumeItem{Designed clean error handling and notifications for join/leave events, boosting user clarity and trust.}
\end{itemize}

\vspace{6pt}

\textbf{FileDrive - Cloud File Storage Backend} \hfill \href{https://github.com/mohankumarkadiri/File-Drive}{GitHub}
\vspace{6pt}
\begin{itemize}[leftmargin=*,itemsep=2pt]
  \resumeItem{Developed a secure, Google OAuth 2.0-authenticated cloud file storage backend using Node.js, Express, MongoDB, Redis, and AWS S3.}
  \resumeItem{Implemented hierarchical folder management with materialized-path schema, enabling deep folder nesting and sub-100ms directory listings.}
  \resumeItem{Built fine-grained per-user access control (OWNER/EDITOR/VIEWER) at both file and folder levels with dynamic permission updates.}
  \resumeItem{Enabled secure file operations: upload, streaming downloads, move to Trash (soft-delete), permanent deletion, and duplicate prevention.}
  \resumeItem{Automated Trash cleanup with cron jobs, configurable retention, and storage reclamation (~10\% of storage).}
  \resumeItem{Created shareable links with expirable tokens for team collaboration while enforcing role-based permissions.}
  \resumeItem{Stateless servers architected for horizontal scaling behind a load balancer.}
\end{itemize}

\vspace{6pt}

\textbf{Env-Lens - VS Code Extension} \hfill
GitHub: https://github.com/mohankumarkadiri/env-lens \textbar{} Marketplace: https://marketplace.visualstudio.com/items?itemName=mohankumarkadiri.env-lens&ssr=false
\vspace{3pt}
\begin{itemize}[leftmargin=*,itemsep=2pt]
  \resumeItem{Built VS Code extension for inline hover previews of environment variables via \texttt{process.env.*}.}
  \resumeItem{Auto-loads \textbf{1000+} workspace \texttt{.env} variables, eliminating manual lookups and improving debugging speed by \textbf{~30\%}.}
  \resumeItem{Published on VS Code Marketplace, reaching \textbf{5+ installs} in one day.}
\end{itemize}

%===== SKILLS =====
\section*{Skills}
\begin{itemize}[leftmargin=*,itemsep=2pt]
  \resumeItem{\textbf{Languages:} Python, C++, JavaScript}
  \resumeItem{\textbf{Backend:} Node.js, Express, Django, REST APIs, AWS Lambda, Docker}
  \resumeItem{\textbf{Frontend:} React.js, HTML, CSS}
  \resumeItem{\textbf{Databases:} MongoDB, MySQL, PostgreSQL, Redis}
  \resumeItem{\textbf{Tools/Platforms:} Git, Socket.IO, AWS, GCP, Osquery}
  \resumeItem{\textbf{Expertise:} System Design, Scalable Architectures, Security Engineering, Algorithms}
\end{itemize}

%===== COMPETITIVE PROGRAMMING =====
\section*{Competitive Programming}
\begin{itemize}[leftmargin=*,itemsep=2pt]
  \resumeItem{LeetCode: Guardian badge (550+ problems, \textbf{top 1\%})}  
  \resumeItem{HackerRank: \textbf{6-star} coder}  
  \resumeItem{Google Kick Start: Global Rank \textbf{\#3442}}
\end{itemize}

%===== EDUCATION =====
\section*{Education}
\textbf{National Institute of Technology, Andhra Pradesh} \hfill May 2023\\
B.Tech in Computer Science and Engineering\\
CGPA: \textbf{8.13/10}

\vspace{4pt}
\textbf{Relevant Courses:} Data Structures, Algorithms, Operating Systems, Computer Networks, DBMS, Distributed Systems, OOPS.

%===== INTERESTS =====
\section*{Interests}
\begin{itemize}[leftmargin=*,itemsep=2pt]
  \resumeItem{Chess}
  \resumeItem{Music}
  \resumeItem{Fitness}
\end{itemize}

\end{document}